Dominance Regions for Imaginary $\bfg$-vectors

### 2020-08-15 dominance_regions.tex
Added rough inequalities
Correct inequalities, finally!
Refactored your inequalities into a (hopefully) more intuitive form
Some more equivalent forms, playing the same game with the last two does not seem to produce nice results, are the signs correct in the numerators of the $\lambda$ terms?
Another proposal
Recording some thoughts in a new section, 'total domination' sounds really cool

\newcommand{\cC}{\mathcal{C}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cQ}{\mathcal{Q}}

@@

  For $t\in\TT_n$, define $\phi^t_k:\ZZ^n\to\ZZ^n$ as the piecewise-linear map
  \[\phi^t_k(\lambda)=\begin{cases} E^t_{k,+}\lambda & \text{if $\lambda_k\ge0$;}\\ E^t_{k,-}\lambda & \text{if $\lambda_k<0$;} \end{cases}\]
  where the entries of $E^t_{k,\varepsilon}$ is given by \eqref{eq:mutation matrix} with $b^t_{ij}$ in place of $b_{ij}$.
  We leave it as an exercise for the reader to check that $(\phi^t_k)^{-1}=\phi^{t'}_k$ whenever $t,t'\in\TT_n$ are joined by an edge labelled $k$.
  For $t\in\TT_n$, define the piecewise-linear automorphisms $\phi_t:\ZZ^n\to\ZZ^n$ by
  \begin{itemize}
    \item $\phi_{t_0}=\Id$;
    \item if $t,t'\in\TT_n$ are joined by an edge labelled $k$, then $\phi_{t'}=\phi^t_k \phi_t$.
  \end{itemize}
  For $\lambda\in\ZZ^n$, define the \emph{$B_t$-cone} $\cC_t(\lambda):=\lambda+B_t\cdot\RR_{\ge0}^n$ pointed at $\lambda$.
  \begin{definition}
    For $\lambda\in\ZZ^n$, define the \emph{dominance polytope} 
    \[ \cP(\lambda) = \bigcap_{t\in\TT_n} \phi_t^{-1} \cC_t(\phi_t \lambda). \]
  \end{definition}
  Our goal is to understand the dominance polytopes $\cP(\lambda)$ for all $\lambda$.

@@

>>>>

\newcommand{\cC}{\mathcal{C}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cQ}{\mathcal{Q}}

@@

  (DR: I changed to $\RR$ because it didn't seem like we really cared about integer points at the moment, when we try to link up with minors this will need to be added.)
  For $t\in\TT_n$, define $\phi^t_k:\RR^n\to\RR^n$ as the piecewise-linear map
  \[\phi^t_k(\lambda)=\begin{cases} E^t_{k,+}\lambda & \text{if $\lambda_k\ge0$;}\\ E^t_{k,-}\lambda & \text{if $\lambda_k<0$;} \end{cases}\]
  where the entries of $E^t_{k,\varepsilon}$ is given by \eqref{eq:mutation matrix} with $b^t_{ij}$ in place of $b_{ij}$.
  We leave it as an exercise for the reader to check that $(\phi^t_k)^{-1}=\phi^{t'}_k$ whenever $t,t'\in\TT_n$ are joined by an edge labelled $k$.
  For $t\in\TT_n$, define the piecewise-linear automorphisms $\phi_t:\RR^n\to\RR^n$ by
  \begin{itemize}
    \item $\phi_{t_0}=\Id$;
    \item if $t,t'\in\TT_n$ are joined by an edge labelled $k$, then $\phi_{t'}=\phi^t_k \phi_t$.
  \end{itemize}
  For $\lambda\in\RR^n$, define the \emph{$B_t$-cone} $\cC_t(\lambda):=\lambda+B_t\cdot\RR_{\ge0}^n$ pointed at $\lambda$.
  \begin{definition}
    For $\lambda\in\RR^n$, define the \emph{dominance polytope} 
    \[ \cP(\lambda) = \bigcap_{t\in\TT_n} \phi_t^{-1} \cC_t(\phi_t \lambda). \]
    When $\mu\in\cP(\lambda)$, we say \emph{$\lambda$ dominates $\mu$}.
  \end{definition}
  Our goal is to understand the dominance polytopes $\cP(\lambda)$ for all $\lambda$.
  \begin{lemma}
    The sets $\cP(\lambda)$ are actually polytopes.
  \end{lemma}

@@

  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by the following six inequalities:
  \begin{align}
    -\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1+\lambda_2-\frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1 - \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x-\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1-\frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}x-y\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c-\sqrt{b c (b c-4)}}{2 c}y\geq0
  \end{align}
  Are any of these better forms?
  \begin{align}
    (x-\lambda_1)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    \nonumber \iff \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2)\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    \nonumber \iff -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    \nonumber \iff -b\lambda_2 + (x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+(x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    \nonumber \iff c\lambda_1+\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+b\lambda_2+(x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
  \end{align}
  Another proposal (I also changed the order of the equations)
  \begin{align}
    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2 
    \\
    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2
    \\
    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
    \\
    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1
    \\
    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1-b\lambda_2
  \end{align}

  \section{The Total Domination Polyhedron}

  Define the \emph{total domination polyhedron} $\cD:=\{(\lambda,\mu):\mu\in\cP(\lambda)\}$, i.e. this is the set of all pairs where $\lambda$ dominates $\mu$.
  Write $\pi_1:\cD\to\RR^n$ for the projection to $\lambda$ and $\pi_2:\cD\to\RR^n$ for the projection to $\mu$.
  \begin{itemize}
    \item Is it a polyhedron?
    \item The lemma below might suggest so.  
      Indeed, if it is, by the Decomposition Theorem, we can write $\cD$ as the Minkowski sum of a polyhedral cone (almost certainly $\cI$) and a convex polytope (what is it?).
      I am ignoring that it should really be the union of this polyhedron with a plane if the previous sentence holds any water.
    \item Actually, we might need to take the union of several polyhedra to account for the variations in the fibers $\pi_1^{-1}(\lambda)$.
  \end{itemize}

  Is the following result true beyond rank 2?
  \begin{lemma}
    For $\mu\in\RR^2$, $\pi_2^{-1}(\mu)$ is a translate of the imaginary cone $\cI$ or the union of such with a single point.
  \end{lemma}
  \begin{proof}
    Maybe the vertex of this cone is given by $\lambda=(\lambda_1,\lambda_2)$ where
    \[\lambda_1=\frac{2b\mu_2-4\mu_1}{bc-4+\sqrt{bc(bc-4)}} \qquad \text{and} \qquad \lambda_2=\frac{2c\mu_1-4\mu_2}{bc-4+\sqrt{bc(bc-4)}}.\]
  \end{proof}
